Development of a 3D display

### 2016-05-18 paper.tex
Added space after "Vdd"

The supply lines are placed beneath the row of LEDs. Had I placed the supply on the upper edge of
the board, I still would've had to connect all the 16 anodes to \vdd. The driver chips, on the
other hand, only need one connection to \vdd and GND each, so by placing the supply lines at the
bottom of the board I have less traces running across the board vertically.

>>>>

The supply lines are placed beneath the row of LEDs. Had I placed the supply on the upper edge of
the board, I still would've had to connect all the 16 anodes to \vdd. The driver chips, on the
other hand, only need one connection to \vdd\ and GND each, so by placing the supply lines at the
bottom of the board I have less traces running across the board vertically.
